### 2021-07-09 paper/ase21/eval.tex
Fixed minor number typo in eval.tex

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:life} illustrates the life spans of true bugs;
Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
Among 93 true bugs, 48 bugs are \textit{inherited},
which means that they are created before 2018,
and 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of 14 newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that 48 inherited bugs are created on January 1, 2018,
the average life span is 414.5 and the maximum life span is 1,164.
All the bugs with the maximum life span are inherited ones and they are all newly detected.

>>>>

To understand the impact of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{life span} of a bug denotes
the number of days between the created date and the resolved date.
Figure~\ref{fig:life} illustrates the life spans of true bugs;
Figure~\ref{fig:life}(a) depicts the life spans sorted by creation and
Figure~\ref{fig:life}(b) depicts the histogram of the life spans in a logarithmic scale.
Among 93 true bugs, 49 bugs are \textit{inherited},
which means that they are created before 2018.
Moreover, 14 bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of 14 newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that 49 inherited bugs are created on January 1, 2018,
the average life span is 422.8 and the maximum life span is 1,164.
All the bugs with the maximum life span are inherited ones and they are all newly detected.
